\FOT{3}\Node%
{}\Node%
{\def\Element%
{0:0}}  \Node%
{\def\Element%
{0:1}}    \Node%
{\def\Element%
{0:2}}example driver manual\endNode{}
    \Node%
{\def\Element%
{0:3}}A libdbi driver providing connectivity to Example databases using libexampleclient.\endNode{}
  \Node%
{\def\Element%
{0:4}}      \Node%
{\def\Element%
{0:5}}E.\endNode{}
      \Node%
{\def\Element%
{0:6}}X.\endNode{}
      \Node%
{\def\Element%
{0:7}}Ample\endNode{}
      \Node%
{\def\Element%
{0:8}}	\Node%
{\def\Element%
{0:9}}\Node%
{\def\Element%
{0:10}}example@users.sourceforge.net\endNode{}\endNode{}
      \endNode{}
    \endNode{}
    \Node%
{\def\Element%
{0:11}}      \Node%
{\def\Element%
{0:12}}	\Node%
{\def\Element%
{0:13}}0.1\endNode{}
	\Node%
{\def\Element%
{0:14}}2002-\/11-\/5\endNode{}
      \endNode{}
    \endNode{}
  \endNode{}
  \Node%
{\def\Element%
{0:15}}    \Node%
{\def\Element%
{0:16}}Preface\endNode{}
    \Node%
{\def\Element%
{0:17}}\Node%
{\def\Element%
{0:18}}libdbi\endNode{} is a database abstraction layer written in C. It implements a framework that can utilize separate driver libraries for specific database servers. The \Node%
{\def\Element%
{0:19}}libdbi-\/drivers\endNode{} project provides the drivers necessary to talk to the supported database servers.\endNode{}
    \Node%
{\def\Element%
{0:20}}This manual provides information about the Example driver. The manual is intended for programmers who write applications linked against libdbi and who want their applications to work with the Example driver.\endNode{}
    \Node%
{\def\Element%
{0:21}}Questions and comments about the Example driver should be sent to the \Node%
{\def\Element%
{0:22}}libdbi-\/drivers-\/devel\endNode{} mailing list. Visit the \Node%
{\def\Element%
{0:23}}libdbi-\/drivers-\/devel list page\endNode{} to subscribe and for further information. Questions and comments about the libdbi library should be sent to the appropriate libdbi mailing list.\endNode{}
    \Node%
{\def\Element%
{0:24}}The Example driver is maintained by \Node%
{\def\Element%
{0:25}}E.X. Ample\endNode{}.\endNode{}
  \endNode{}
  \Node%
{\def\Element%
{0:26}}    \Node%
{\def\Element%
{0:27}}Introduction\endNode{}
    \Node%
{\def\Element%
{0:28}}\endNode{}
  \endNode{}
  \Node%
{\def\Element%
{0:29}}    \Node%
{\def\Element%
{0:30}}Installation\endNode{}
    \Node%
{\def\Element%
{0:31}}\endNode{}
    
    
  \endNode{}
  \Node%
{\def\Element%
{0:32}}    \Node%
{\def\Element%
{0:33}}Driver options\endNode{}
    \Node%
{\def\Element%
{0:34}}\endNode{}
  \endNode{}
  \Node%
{\def\Element%
{0:35}}    \Node%
{\def\Element%
{0:36}}Peculiarities you should know about\endNode{}
    \Node%
{\def\Element%
{0:37}}\endNode{}
  \endNode{}\endNode{}\endNode{}\endFOT{}